---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(tidyverse)
library(polite)
library(rvest)
library(cancensus)
library(haven)
```

# Loading client data

```{r}
cust_dev<- read_rds("data-raw/cust_dev.Rds")
customer<- read_rds("data-raw/customer.Rds")
#load data
cust_sleep<- read_rds("data-raw/cust_sleep.Rds")

device<- read_rds("data-raw/device.Rds")
```

# Getting external data

## Web scraping industry data

```{r}
url <- "https://fitnesstrackerinfohub.netlify.app"

# Make sure this code is updated appropriately to provide 
# informative user_agent details
target <- bow(url,
              user_agent = "ellazhang.zhang@utoronto.ca for STA303/1002 project",
              force = TRUE)

# Any details provided in the robots text on crawl delays and 
# which agents are allowed to scrape
target

html <- scrape(target)

device_data <- html %>% 
  html_elements("table") %>% 
  html_table() %>% 
  pluck(1) # added, in case you're getting a list format
```

# Census API

```{r}
options(cancensus.api_key = "CensusMapper_307a081ba8f2a9c0c32cb9240f89bbf2",
        cancensus.cache_path = "cache") # this sets a folder for your cache

# get all regions as at the 2016 Census (2020 not up yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # Figure out what CSD means in Census data
  as_census_region_list()

# This can take a while
# We want to get household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD')

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)
```

#Post code conversion
```{r}
dataset = read_sav("data-raw/pccfNat_fccpNat_082021sav.sav")

postcode <- dataset %>% 
  select(PC, CSDuid)
```

#merge data
```{r}
postcode_income<- postcode %>% distinct(PC,.keep_all=TRUE)%>%
  left_join(median_income, by="CSDuid")
  #repeated postcode value with same CSDuid
  #default way to choose the first value

customer_data<- customer %>% left_join(cust_dev, by="cust_id")%>%
  left_join(device, by="dev_id")
#join the device data

customer_data<- customer_data%>% left_join(postcode_income, by= c("postcode"="PC"))%>%
  select(-pronouns, -released)
#combine customer_data with postcode_income 
#eliminate CSDuid, same with postcode
#duplicated info, eliminate pronouns

customer_data<- customer_data %>% filter(!is.na(sex))%>%
  mutate(age =2022-as.numeric(substr(dob,1,4)))%>% select(-dob)
#use dob calculate the age of customer
#duplicated info, eliminate dob

customer_data<- customer_data %>%
  mutate(skin_color= case_when(emoji_modifier=="U+1F3FF"~"Dark",
                         emoji_modifier=="U+1F3FD"~"Medium",
                         emoji_modifier=="U+1F3FC"~"Medium~Light",
                         emoji_modifier=="U+1F3FB"~"Light",
                         emoji_modifier=="U+1F3FE"~"Medium~Dark",
                         is.na(emoji_modifier)~"Default")) %>%
           select(-emoji_modifier)
#through emoji_modifier know their skin color
#duplicated info, eliminate emoji_modifier

write_rds(customer_data,"/Users/LuHongTu/Desktop/0-Tuo/303final/data/customer_data.Rds")
write_rds(cust_sleep,"/Users/LuHongTu/Desktop/0-Tuo/303final/data/cust_sleep.Rds")
#export the data as rds
```

